\documentclass[11pt,letterpaper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{green}

\usepackage[margin=1.2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{parcolumns}
\usepackage{ragged2e} % For ragged right text formatting

% Personal info
\name{Edward}{Jiménez M.}
\title{Senior Software Engineer · Cloud \& Backend}
\address{Bogotá, Colombia}{}
\phone[mobile]{+57~(301)~773~5242}
\email{eddy@eddyjim.com}
\homepage{www.eddyjim.com}
\social[linkedin]{eddyjim}
\social[github]{eddyjim}
\quote{Cloud-native systems, end-to-end.}

\begin{document}
	
	\makecvtitle
	
	% Summary
	\section*{Summary}
	Senior software engineer with 10+ years building cloud-native systems on AWS. Currently at BriteCore (insurance SaaS) shipping event-driven services, a state-machine billing engine and an AI agent for policy summarization. Earlier: led the design and implementation of a serverless LTI service that decoupled the Blackboard LMS monolith, and built the PoC seeding an MVC monolith-to-microservices migration at Alkanza. Strong in Python and full-stack with Vue/React.
	
	\begin{parcolumns}[colwidths={1=0.65\textwidth, 2=0.30\textwidth}]{2}
		
		\colchunk{%
			\section{Tech Stacks}
			\cvitem{Languages}{\begin{tabular}[t]{@{}l@{}}Python, Java, JavaScript, TypeScript, Ruby, Bash\end{tabular}}
			\cvitem{Backend Frameworks}{\begin{tabular}[t]{@{}l@{}}Flask, FastAPI, Starlette, Falcon, Express, Rails, Spring Boot\end{tabular}}
			\cvitem{Frontend Frameworks}{\begin{tabular}[t]{@{}l@{}}React, Vue, Angular, Astro, Bootstrap, Material\end{tabular}}
			\cvitem{Databases}{\begin{tabular}[t]{@{}l@{}}PostgreSQL, MySQL, MongoDB, Oracle, SQL Server\end{tabular}}
			\cvitem{DevOps/CI-CD}{\begin{tabular}[t]{@{}l@{}}Docker, Kubernetes, GitHub Actions, Jenkins, Terraform\end{tabular}}
			\cvitem{Cloud}{\begin{tabular}[t]{@{}l@{}}AWS (Lambda, API Gateway, S3, DynamoDB, Step Functions, CodeBuild,\\Kinesis, CloudWatch, Xray), Tray.io\end{tabular}}
			\cvitem{Tools}{\begin{tabular}[t]{@{}l@{}}Git, Figma, Postman, JIRA\end{tabular}}
		}
		
		\colchunk{%
			\section{Experience}
			\raggedright
			\cventry{2022--Pres.}{\parbox[t]{\linewidth}{Fullstack Engineer}}{\parbox[t]{\linewidth}{Team International {\footnotesize(BriteCore)}}}{}{}{}
			\cventry{2020}{\parbox[t]{\linewidth}{Technical Lead}}{Blackboard}{}{}{}
			\cventry{2018}{\parbox[t]{\linewidth}{Senior Software\newline Engineer}}{Alkanza}{}{}{}
			\cventry{2016}{\parbox[t]{\linewidth}{Software Architect}}{Banking Technologies\newline Solutions S.A.S}{}{}{}
			\cventry{2015}{\parbox[t]{\linewidth}{Oracle EBS\newline Architect}}{Hardnetics LTDA}{}{}{}
			\cventry{2015}{\parbox[t]{\linewidth}{Senior Consultant}}{Fussion Corporation SAS}{}{}{}
			\cventry{2013}{\parbox[t]{\linewidth}{Functional / Technical\newline Consultant}}{Soaint SAS}{}{}{}
		}
		
		\end{parcolumns}
		
		
	% Projects
	\section{Relevant Projects}
	\cvitem{Insurance Policy AI Agent}{Built an AI agent on the BriteCore platform that produces summarized views of insurance policies, reducing manual policy-lookup time for end users.}
	\cvitem{Serverless LTI Integration}{Migrated LMS integration to a serverless AWS stack including deployment pipelines.}
	\cvitem{Monolith Split}{Built the PoC validating an MVC monolith migration to an event-based cloud architecture; contributed to the implementation rollout.}
	
	
	% Education
	\section{Education}
	\cventry{2017}{Master of IT Architectures}{Universidad de Los Andes}{Bogotá}{}{Master}
	\cventry{2013}{Software Engineer}{Escuela Colombiana de Ingeniería}{Bogotá}{}{Bachelor}
	
\end{document}
